The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-10 Writeup/paper_v3.tex
Major concerns addressed. Fine tuning of plots remains

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G}}
\newcommand{\mi}{\ensuremath{M_I}}
\newcommand{\sersicn}{S\'{e}rsic $n$ }
\newcommand{\sersic}{S\'{e}rsic }
\newcommand{\btt}{Bulge-to-Total }

@@

\rachel{Overall comment: the figures need a {\em lot} of work.  First,
  they should be in the same order as they are referenced in the
  text.  Second, they need to be sensibly referenced in the text; you
  can't say ``as we see\dots'' without having a clear statement that
  we should be looking at Fig.~4 (or whatever).  In all
  cases, the font size is way too small, so you should enlarge it.
  The rule of thumb for MNRAS and other journals is that the font size
  in the figures should appear the same size as the font in the text
  of the paper.  (This is true for axis labels, tick labels, and text
  in the legend.)  You also need to write good captions, because some
  people will not really read the paper, just the captions.  MNRAS
  does not use the subfigure environment, so you should remove it.
  Just have the figures on top of or next to each other, and then in
  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}

\section{Introduction}
\label{S:intro}

\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.  I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

Previous studies have shown that any shape measurement method that uses second moments cannot be independent of the morphology and substructure of the galaxies involved. ({\bf rephrased from GREAT3}).
Hence, it is important to check any method that is proposed to measure the shape of the galaxies to check against a simulation that generates images as realistic as possible.  
With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in \S\ref{S:data}.
While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
It is known {\bf cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
observed in the COSMOS' field of view may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.

@@

 \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
                                       {\bf copied from Mandelbaum 2011.}
\end{enumerate}
%\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}

@@

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. \rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

Stellar mass estimates were obtained~\citep{COSMOS_XRAY} using the Bayesian code described in~\cite{KEVIN_MSTAR}. Basically, a grid of models that vary in age, star formation history, dust content and metallicity
are constructed to which the observed galaxy's spectral energy distribution (SED) and the photometric redshift are referenced to. At each grid point, the probability that the 
SED fits the model are calculated and by marginalizing over all the parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
is taken as the stellar mass estimate. A Chabrier IMF is assumed.

@@

In order to study the variation in the intrinsic ellipticity distribution and other morphological indicators with environment, there are three main steps to be carried out.
\begin{enumerate}
 \item To identify overdense and underdense environments in our survey from the redshift distribution of galaxies (\S\ref{sub:overdensities}),
 \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}),
 \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting})
\end{enumerate}

@@

Weak lensing simulations will use galaxies selected in 2D redshift slices and
we split our sample in a similar way to assign overdensities.
\rachel{You need a clear and unambiguous statement here as to whether
  or not you are using flux-limited or volume-limited samples.  If the
  latter, then the section on volume-limiting needs to come {\em
    before} this one!  As is, you definitely refer to volume-limiting
  later in this subsection, so the volume-limiting subsection has to
  go first.}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) = cz^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) = az^2\exp{(-bz^{1.5})}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the redshift histograms. Here $a,b$ and $c$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
\rachel{Were you going to use other fitting functions as a test of the
  method?  If so, you should introduce them here.}

The curves are normalized such that the area under the curves is equal to the number of galaxies considered.
{\bf Fig 3 - Histogram with fits }. \\
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
\end{figure}

Overdensity in a redshift bin is defined as the ratio of the
difference between the value given by the histogram and the value
predicted by the model to the latter:
\begin{equation}
\delta=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
\end{equation}
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.

@@

We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.

We use therefore relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness. This increases the sample size significantly, from 7,418 galaxies to 11,169.

\subsection{Volume limiting}
\label{sub:volumelimiting}
COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $i$-band magnitudes, denoted as $M_I$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}
Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
We used the published result~\citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
Thus, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier{\bf cite} IMF. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9 {\bf What exactly does this mean?}
\rachel{We discussed this in our meeting, so I think you can fix this.}
As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.

\begin{figure*}
 \centering
 \includegraphics[width=0.66\columnwidth]{SMF1} \
 \includegraphics[width=0.66\columnwidth]{SMF2} \
 \includegraphics[width=0.66\columnwidth]{SMF3}
 \caption{SMF plots \rachel{Legend labels need to be better, e.g., $M_I<25.2$.}}
 \label{fig:smf}
\end{figure*}

There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
enough blank space) intersects with the edge of the CCD.
If all galaxies were the same size, this would be a purely random
effect, but in fact bigger galaxies are more likely to get excluded by
this cut. Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this effect is dominant at lower redshifts. 
Thus, we use the full F814W$\le$23.5 sample, irrespective of the
existence of postage stamps, and believe that our conclusions are not
affected by this bias. \rachel{What do you mean we use the full sample
  $<23.5$?  For what purpose?  We obviously don't use it for the fits
  or shape estimates, so be specific.}

Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting. %Refer to Figure~\ref{fig:comoving_densities}.
And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  \label{fig:redshift_fluxlimited}
  \caption{\rachel{Why does this figure appear again?}}
\end{figure}

@@

\emph{Talk more about environments - Nature and nurture?}

@@

\rachel{This section must end with a clear list of the quantities we
  are using from Claire's fits, and from the re-Gaussianization shear
  estimation routine.}

\section{Results}
\label{S:results}
\rachel{Give a big picture summary of the goal of this section.  You
  are taking the results from the previous section and doing what with
  them, and why?}

>>>>

%More new commands by Arun Kannawadi
\newcommand{\mg}{\ensuremath{M_G}}
\newcommand{\mi}{\ensuremath{M_I}}
\newcommand{\sersicn}{S\'{e}rsic $n$ }
\newcommand{\sersic}{S\'{e}rsic }
\newcommand{\btt}{Bulge-to-Total }
\newcommand{\s}{\ensuremath{\mathcal{S}}}

@@

\rachel{Overall comment: the figures need a {\em lot} of work.  First,
  they should be in the same order as they are referenced in the
  text.  Second, they need to be sensibly referenced in the text; you
  can't say ``as we see\dots'' without having a clear statement that
  we should be looking at Fig.~4 (or whatever).  In all
  cases, the font size is way too small, so you should enlarge it.
  The rule of thumb for MNRAS and other journals is that the font size
  in the figures should appear the same size as the font in the text
  of the paper.  (This is true for axis labels, tick labels, and text
  in the legend.)  You also need to write good captions, because some
  people will not really read the paper, just the captions.  MNRAS
  does not use the subfigure environment, so you should remove it.
  Just have the figures on top of or next to each other, and then in
  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
\arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
\section{Introduction}
\label{S:intro}

\rachel{DES is far from the only survey; since I'm in HSC and the work was supported by Euclid project, it seems strange to only mention DES.  I recommend taking one of my papers (e.g., the one on image simulations from 2012) and lifting the entire list of references to surveys directly from there.}
\arun{Done.}
Major surveys such as the Hyper Suprime-Cam \arun{How to add shortforms?}~\citep{HSC_Overview}, Dark Energy Survey~\citep{DESC}, the KIlo-Degree Survey~\citep{KIDS}, the Panoramic Survey Telescope and Rapid Response System~\citep{PanSTARRS_2010},
the Large Synoptic Survey Telescope~\citep{LSST_Book},Euclid\footnote{http://sci.esa.int/science-e/www/area/index.cfm?fareaid=102}, Wide-Field Infrared Survey Telescope~\citep{WFIRST_Final}
are planned to be carried out over the next decade or two that will gather huge amounts of weak lensing data that can be used to constrain cosmological parameters more precisely than ever.
Weak gravitational lensing probes the nature of dark energy through both the growth of structure in the universe with redshift and the dependence of distances on the expansion rate or the Hubble parameter.
However, most of the matter in the universe is made up of dark matter which cannot be detected by most of the standard astronomical/cosmological probes. Weak lensing happens to be the cleanest probe for this purpose.
As light from the background sources passes through the foreground cluster of galaxies and dark matter profiles, the shapes get distorted. Weak lensing also causes magnification in addition to introducing a shear.
%Weak lensing effects need to be removed from the Cosmic Microwave Background (CMB) analysis to understand the initial conditions of the universe.

@@

Previous studies have shown that any shape measurement method that uses second moments cannot be independent of the morphology and substructure of the galaxies involved. ({\bf rephrased from GREAT3}).
Hence, it is important to check any method that is proposed to measure the shape of the galaxies to check against a simulation that generates images as realistic as possible.  
With this in mind, the GREAT3 challenge~\citep{great3} was held with the aim to test and faciliate methods for measuring weak gravitational lensing by analyzing astronomical images.
Software packages like GalSim\footnote{https://github.com/GalSim-developers/GalSim} can generate galaxy images fairly accurately, given realistic input parametes.
The training dataset used in the challenge comes from the COSMOS survey, which we describe in sufficient detail in \S\ref{S:data}.
While providing a good quality (high $S/N$) images to be trained over, there could be some bias introduced due to the survey being a narrow one.
It is known \arun{cite refs.} that the shape and morphology of galaxies depend very much on their local environment. Hence, local overdensities or underdensities
observed in the COSMOS' field of view (FOV) may cause the properties of the galaxies to be associated with the redshift, thus unable to distinguish between redshift evolution and large scale structure.

@@

 \item \texttt{GOOD\_ZPHOT\_SOURCE=1}: This cut requires that there be a good photometric redshift, which typically is equivalent to requiring that the galaxy not be located within
                                       the masked regions of the Subaru $BVIz$ imaging used for photometric redshifts, and that it have a successful match against an object in the Subaru imaging
                                       \arun{copied from Mandelbaum 2011.}
\end{enumerate}
%\rachel{The cuts you just gave are really basic or fundamental ones.  Those should go before any discussion of more complicated derived quantities like redshifts, stellar mass, Sersic fits, etc.}

@@

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for F814W $\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. F814W $\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5. However, we will use F814W$\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.  We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
\rachel{Make a clear and explicit statement that we always require $z<1$ (or is it $1.2$?), we require the MAG\_AUTO in F814W to be $<23.5$, and we use the parent sample that goes to $25.2$ for stellar masses and luminosities only.}
\arun{Done.}
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

Stellar mass estimates were obtained~\citep{COSMOS_XRAY} using the Bayesian code described in~\cite{KEVIN_MSTAR}. Basically, a grid of models that vary in age, star formation history, dust content and metallicity
are constructed to which the observed galaxy's spectral energy distribution (SED) and the photometric redshift are referenced to. At each grid point, the probability that the 
SED fits the model are calculated and by marginalizing over all the parameters in the grid, the stellar mass probability distribution is obtained. The median of this distribution
is taken as the stellar mass estimate. A Chabrier IMF~\citep{ChabrierIMF} is assumed.

@@

In order to study the variation in the intrinsic ellipticity distribution and other morphological indicators with environment, there are three main steps to be carried out.
\begin{enumerate}
 \item To identify overdense and underdense environments in our survey from the redshift distribution of galaxies (\S\ref{sub:overdensities}),
 \item To limit the sample such that Malmquist bias is minimized before comparing galaxies in different redshift slices (\S\ref{sub:volumelimiting}),
 \item To estimate the galaxy axis ratios and other morphological indicators such as  \sersic index and Bulge-to-Total ratios (\S\ref{sub:axisratio}).
\end{enumerate}

@@

Weak lensing simulations will use galaxies selected in 2D redshift slices and
we split our sample in a similar way to assign overdensities.
\rachel{You need a clear and unambiguous statement here as to whether
  or not you are using flux-limited or volume-limited samples.  If the
  latter, then the section on volume-limiting needs to come {\em
    before} this one!  As is, you definitely refer to volume-limiting
  later in this subsection, so the volume-limiting subsection has to
  go first.}
\arun{It should be overdensities followed by volume limiting section. I believe there is no ambiguity now and read this paragraph a couple of times to verify that.}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) = cz^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) = az^2\exp{(-bz^{1.5})}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the redshift histograms. Here $a,b$ and $c$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}

%The curves are normalized such that the area under the curves is equal to the number of galaxies considered. - no longer true if not using fithist.c

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited (F814W$\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_fluxlimited}
\end{figure}

Overdensity in a redshift bin is defined as the ratio of the
difference between the value given by the histogram and the value
predicted by the model to the latter:
\begin{equation}
\delta=\frac{(N-N_{\text{mod}})}{N_{\text{mod}}}.  
\end{equation}
%(\rachel{This $\delta$ definition is important, so it should be in an equation environment.})
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `neutral regions'.

@@

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified. Although, the $z=0.40-0.55$ bin
appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $I$-band magnitudes, denoted as $M_I$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be  self-consistent throughout the text.}\arun{I think they call it $I_{814}$, so $I$.}
Since the parent sample contains fainter galaxies, upto F814W=25.2, we compare the distribution of the F814W=23.5 sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

%We see that the region between $0.85<z<1.0$ is neither overdense nor underdense according to our model and hence is not going to be considered for further analysis.
The region between $0.85<z<1.0$ is only moderately overdense and we do not seem to have as many underdense regions to compare with. It would rather be advantageous to disregard this region
and redo the volume limiting procedure.
We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We choose to impose the cut at $M_I=-20.8$, with 95.3\% completeness in the $0.8 < z \le 0.85$ bin. This increases the sample size significantly, from 7,418 galaxies to 11,169. We call this sample \s$1$.

However, previous studies {\bf cite} have shown that absolute luminosities evolve with redshift. Thus, we must also let the luminosity cut evolve with the redshift. 
There has been no published literature on the LF for the $I$-band, particularly for the COSMOS survey.
We used the published result~\citep{Faber2007} for the `rate' of evolution of B-band magnitudes for DEEP2 and COMBO-17 surveys, which is $ \Delta M_B^* \sim -1.23$ mag per unit redshift, for both blue and red galaxies combined together.
Typically, estimates of evolution in K-band are lesser than the estimates of evolution in B and V bands.
Assuming that the evolution is a smooth function of the wavelength, the evolution in I-band is expected to be lesser than that of the B-band. 
Therefore, by considering no evolution and an upper bound on the evolution, we can interpolate what the results would be like for the true $I$-band evolution.

Thus, we construct a second volume-limited sample \s$2$, this time by letting the luminosity cut evolve. Starting from $M_I = -20.8$ for the $0.8<z\le0.85$ bin, we add to it $1.23$ times the difference between the
bincenters to obtain the luminosity cut for the other (lower) redshift bins. At lower redshifts, we allow for fainter galaxies that wouldn't have passed the cut in \s$1$ and hence has more galaxies.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_I$ s, we compare the stellar mass in the F814W$\le$23.5 sample with that of the F814W$\le$25.2 sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.

\rachel{Tables need to be in a table environment, with a caption.  Also, you should include the uncategorized slices in here.} \arun{Done.}
\begin{table} 
\centering
\begin{tabular}{|r|c|c|c|c|}
 \hline
 Redshift & Environment & \s$1$ & \s$2$ & \s$3$ \\
 \hline
 0.3-0.4 & Overdense & 1726 & 2505 & 1260 \\
 0.4-0.475 & Neutral & 988 & 1317 & 710 \\
 0.475-0.55 & Neutral & 1410 & 1788 & 902 \\
 0.55-0.65 & Underdense & 1797 & 2193 & 1183 \\
 0.65-0.75 & Overdense & 4059 & 4476 & 2593 \\
 0.75-0.8 & Underdense & 1159 & 1196 & 675 \\
 0.8-0.85 & Overdense & 2428 & 2428 & 1630 \\
\end{tabular}
\caption{List of different redshift bins, their environmental classification and the number of galaxies in them for 3 different ways of constructing a volume-limited sample. See text for more details.}
\label{table:GalaxyCounts}
\end{table}

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{figure_generated}
 \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
          a study of SMF in the same FOV \citep{Tomczak_SMF}. At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range. The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

There is a minor pitfall with this method. We analyse only those galaxies for which postage stamp images exist.
12\% of galaxies that pass our cuts do not have an associated postage stamp image.
Yet, we use the full F814W$\le$23.5 sample, irrespective of the existence of postage stamps, for identifying overdensities and in the completeness calculation for volume-limiting.
\rachel{What do you mean we use the full sample  $<23.5$?  For what purpose?  We obviously don't use it for the fits  or shape estimates, so be specific.}
\arun{Added saying we use the full sample for overdensity calculation and for volume-limiting.}
Postage stamps may not exist because, given the size of the galaxy, the size of the postage stamp we want to draw around it (including enough blank space) intersects with the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
Typically galaxies that are nearby and intrinsically very bright do not have postage stamps associated with them and this is an effect that is dominant at lower redshifts. 
Our completeness calculation is done at high redshifts and thus we believe that our conclusions are not affected by this bias.

%Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting. %Refer to Figure~\ref{fig:comoving_densities}.
%And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

The functional forms for the (flux-limited) redshift distribution that we used in \S\ref{sub:overdensities} are not physically motivated. We fit them again to the  
redshift distribution of a volume-limited sample (\s$1$). Referring to Fig.~\ref{fig:redshift_vollimited}, the values of $\delta$ for the $z=0.40-0.55$ bin have increased and are within $\pm 10\%$ of 0. This is the reason why in \S\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in \S\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$) \s$1$ sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_vollimited}
\end{figure}

@@

\arun{Talk more about environments - Nature and nurture?}

@@

The quantities that we would use from the single \sersic profile fits are the \sersic index and axis ratio
and from the bulge+disk fits will be the \btt ratio given by ${\Sigma_{1/2}(n=4)}/{\left(\Sigma_{1/2}(n=4)+\Sigma_{1/2}(n=1)\right)}$.

\rachel{This section must end with a clear list of the quantities we
  are using from Claire's fits, and from the re-Gaussianization shear
  estimation routine.} \arun{It does.}
